Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-19 paper_io_sim.tex
Fixed concurrent experiment text

            The page cache model notably reduced \wrench's simulation error
            for concurrent applications executed with local I/Os
            (Figure~\ref{fig:multi_local}). For reads, \wrench-cache still
            slightly overestimated reality, due to the discrepancy between
            simulated and real read bandwidths mentioned before. For
            writes, \wrench-cache correctly retrieves the plateau ending at
            \tristan{x} concurrent applications in real life, corresponding
            to the limit beyond which the page cache was saturated with
            dirty data and needed flushing.

            \begin{figure}[b]
                \begin{subfigure}{0.95\linewidth}
                    \centering
                    \includegraphics[width=\linewidth]{result/nighres/figures/nighres_errors.pdf}
                \end{subfigure}
                \caption{Real application results (\textit{Exp 4}) \tristan{increase font size}}
                \label{fig:nighres}
                \end{figure}
        \subsection{Remote storage (Exp 3)}

>>>>

            The page cache model notably reduced \wrench's simulation error
            for concurrent applications executed with local I/Os
            (Figure~\ref{fig:multi_local}). For reads, \wrench-cache
            slightly overestimated runtime, due to the discrepancy between
            simulated and real read bandwidths mentioned before. 
            For writes, \wrench-cache
            retrieved a plateau similar to the one observed in the real
            execution, marking the limit beyond which the page cache was
            saturated with dirty data and needed flushing.

            \begin{figure}[b]
                \begin{subfigure}{0.95\linewidth}
                    \centering
                    \includegraphics[width=\linewidth]{result/nighres/figures/nighres_errors.pdf}
                \end{subfigure}
                \caption{Real application results (\textit{Exp 4})}
                \label{fig:nighres}
                \end{figure}
        \subsection{Remote storage (Exp 3)}
